hormones

### 2020-02-03 analysis/07_hormones.Rmd
now with a summary

a <- fviz_pca_var(res.pca, col.var = "black", title = "Charactherization only") 
# Contributions of variables to PC1

b <- fviz_contrib(res.pca, choice = "var", axes = 1, top = 10) + labs(y = "Dim 1 contibutions (%)",
                                                                      title = element_blank())
# Contributions of variables to PC2
c <- fviz_contrib(res.pca, choice = "var", axes = 2, top = 10) +
  labs(y = "Dim 2 contibutions (%)") + theme(title = element_blank())

plot_grid(a,b,c, nrow = 1, rel_widths = c(1,0.425,0.425), align = "hv")

@@

a <- fviz_pca_var(res.pca, col.var = "black", title = "Charactherization & manipluation") 
# Contributions of variables to PC1

b <- fviz_contrib(res.pca, choice = "var", axes = 1, top = 10) + labs(y = "Dim 1 contibutions (%)",
                                                                      title = element_blank())
# Contributions of variables to PC2
c <- fviz_contrib(res.pca, choice = "var", axes = 2, top = 10) +
  labs(y = "Dim 2 contibutions (%)") + theme(title = element_blank())

plot_grid(a,b,c, nrow = 1, rel_widths = c(1,0.425,0.425), align = "hv")

>>>>

a1 <- fviz_pca_var(res.pca, col.var = "black", title = "Charactherization only") 
# Contributions of variables to PC1

b1 <- fviz_contrib(res.pca, choice = "var", axes = 1, top = 10) + labs(y = "Dim 1 contibutions (%)",
                                                                      title = element_blank())
# Contributions of variables to PC2
c1 <- fviz_contrib(res.pca, choice = "var", axes = 2, top = 10) +
  labs(y = "Dim 2 contibutions (%)") + theme(title = element_blank())

ones <- plot_grid(a1,b1,c1, nrow = 1, rel_widths = c(1,0.425,0.425), align = "hv")

@@

a2 <- fviz_pca_var(res.pca, col.var = "black", title = "Charactherization & manipluation") 
# Contributions of variables to PC1

b2 <- fviz_contrib(res.pca, choice = "var", axes = 1, top = 10) + labs(y = "Dim 1 contibutions (%)",
                                                                      title = element_blank())
# Contributions of variables to PC2
c2 <- fviz_contrib(res.pca, choice = "var", axes = 2, top = 10) +
  labs(y = "Dim 2 contibutions (%)") + theme(title = element_blank())

twos <- plot_grid(a2,b2,c2, nrow = 1, rel_widths = c(1,0.425,0.425), align = "hv")

plot_grid(ones,twos, nrow = 2)
```

# smooth funciton

```{r summary}
head(hormones)
ggplot(hormones, aes(x = as.numeric(treatment), y = plasma_conc, color = hormone)) +
  geom_smooth()

box <- ggplot(hormones, aes(x = as.numeric(treatment), y = plasma_conc)) +
  geom_boxplot(aes(fill = treatment)) +
  #geom_smooth(aes(color = hormone)) +
  facet_wrap(~hormone, scales = "free_y", nrow = 5) +
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16),
                     labels = alllevels) +
  theme_B3() +
  theme(#strip.text = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none",
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = "transparent",colour = NA)) +
  labs(y = "plasma conc. (ng/mL)", x = "parental stage")

line <- ggplot(hormones, aes(x = as.numeric(treatment), y = plasma_conc)) +
  #geom_boxplot(aes(fill = treatment)) +
  geom_smooth(aes(color = hormone)) +
  facet_wrap(~hormone, scales = "free_y", nrow = 5) +
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16),
                     labels = alllevels) +
  theme_B3() +
  theme(#strip.text = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none",
        panel.background = element_rect(fill = "transparent",colour = NA),
        plot.background = element_rect(fill = "transparent",colour = NA)) +
  labs(y = "plasma conc. (ng/mL)", x = "parental stage")

plot_grid(box, line, nrow = 1)
```
